### 2020-10-25 misc/tex-macros/gohlatex-demo.tex
More typos

\algstep B3. [Indicators.] The indicator of an event $\one_A$ equals 1 if $A$ is true and 0 if $A$ is false.
You can also spell out the event; for example if $A$ is the event that $u\edge v$, then you can
write $\indic{u\edge v}$.

@@

\algstep B8. [Operators.] You can make your own operators and functions $\op{myfunc}(x)$ and they can
even have limits, like
$$\limitop{mylim}_{n\to\infty} \op{myfunc}(n).$$

>>>>

\algstep B3. [Indicators.] The indicator of an event $\one_A$ equals 1 if $A$ is true and 0 if $A$ is false.
You can also spell out the event; for example, if $A$ is the event that $u\edge v$, then you can
write $\indic{u\edge v}$.

@@

\algstep B8. [Operators.] You can make your own operators and functions and they can
even have limits, like
$$\limitop{mylim}_{n\to\infty} \op{myfunc}_n(x).$$
